Regular singular Volterra equations on complex domains

### 2023-08-07 reg-sing-volterra.tex
Start switching to 0 and \star for prototype and perturbation parts
Change macro definitions for operator and kernel parts. Switch hand-written
instances to macros. Introduce macros for solution parts, but leave all
instances hand-written for now.

% operator under consideration
\newcommand{\volterra}{\mathcal{V}}
\newcommand{\hardpart}{\mathcal{V}_\text{basic}}
\newcommand{\softpart}{\mathcal{V}_\text{extra}}
\newcommand{\hardker}{k_\text{basic}}
\newcommand{\softker}{k_\text{extra}}

@@

Since $\softpart$ is a holomorphic Volterra operator, $\softker$ is a holomorphic function on $\domain^2$. We'll allow $\softker(a, a')$ to have a simple pole at $\zeta(a) = 0$, like $\hardker(a, a')$ does, but we won't allow any sharper singularity. We'll also put an exponential bound on how fast $\softker$ grows away from the diagonal, mimicking Condition~\eqref{cond:diag-basic} on $\hardker$. Altogether, we'll require:
\begin{itemize}
\condconst{diag}{\epsilon, \lambda_\Delta}\label{cond:eps-lambda} We have
\[ \big| k_\text{extra} (a, a') \big| \leq \textcolor{magenta}{C_k}\frac{|\zeta(a)-\zeta(a')|^\epsilon}{|\zeta(a)|}\,e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\]
over all $a, a' \in \domain$.
\end{itemize}
Notice that this condition prevents $\softker$ from being separable---unless it's zero, of course.

@@

\begin{proof}
    Let $f\in\singexp{\sigma}{\Lambda}$,
    \begin{align*}
        |\zeta(a)|^{-(\sigma+\epsilon)} \, e^{-\Lambda |\zeta(a)|} \, \Big \vert \big[ \softpart f\big](a)\Big\vert
        &\leq |\zeta(a)|^{-(\sigma+\epsilon)}\, e^{-\Lambda |\zeta(a)|} \int_{\zeta=0}^a |k_\text{extra}(a,\cdot)|\, |f| \, |d\zeta| \\
        &\leq |\zeta(a)|^{-(\sigma+\epsilon)}\, e^{-\Lambda |\zeta(a)|} \int_{\zeta=0}^a |k_\text{extra}(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \|f\|_{\sigma,\Lambda} \, |d\zeta| 
    \end{align*}
    By Condition~\eqref{cond:eps-lambda},
    \begin{align*}
         \int_{\zeta=0}^a |k_\text{extra}(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \, |d\zeta| &\leq C_k \int_{\zeta=0}^a \frac{|\zeta(a)-\zeta|^\epsilon}{|\zeta(a)|} e^{\lambda_\Delta |\zeta(a)-\zeta|} |\zeta|^{\sigma}\, e^{\Lambda|\zeta|}\;|d\zeta|\\
         &=C_k |\zeta(a)|^{\epsilon+\sigma} \int_{0}^1 (1-t)^\epsilon e^{\lambda_\Delta |\zeta(a)|(1-t)} t^{\sigma}\, e^{\Lambda|\zeta(a)| t}\;dt\\
         &=C_k |\zeta(a)|^{\epsilon+\sigma}\, e^{\lambda_\Delta |\zeta(a)|}\,  \int_{0}^1 (1-t)^\epsilon  t^{\sigma}\,e^{(\Lambda-\lambda_\Delta)|\zeta(a)| t}\;dt\\
         &\le C_k |\zeta(a)|^{\epsilon+\sigma}\, e^{\lambda_\Delta |\zeta(a)|}\,e^{(\Lambda-\lambda_\Delta)|\zeta(a)|}\int_{0}^1 (1-t)^\epsilon  t^{\sigma}\;dt.
    \end{align*}
    The last step takes advantage of the assumption that $\Lambda \ge \lambda_\Delta$. Recognizing the integral as an evaluation of the beta function, we can rewrite the bound as
    \[ \int_{\zeta=0}^a |k_\text{extra}(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \, |d\zeta| \le C_k |\zeta(a)|^{\epsilon+\sigma}\, e^{\Lambda |\zeta(a)|} \frac{\Gamma(\epsilon+1)\Gamma(\sigma+1)}{\Gamma(\sigma+\epsilon+2)}. \]
    Our assumptions that $\epsilon > 0$ and $\sigma > -1$ ensure that the gamma functions are well-defined. Rearranging to get
    \[ |\zeta(a)|^{-(\epsilon+\sigma)}\, e^{-\Lambda |\zeta(a)|} \int_{\zeta=0}^a |k_\text{extra}(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \, |d\zeta| \le C_k \frac{\Gamma(\epsilon+1)\Gamma(\sigma+1)}{\Gamma(\sigma+\epsilon+2)}, \]
    we conclude that $|\zeta(a)|^{-\sigma-\epsilon} \, e^{-\Lambda |\zeta(a)|} \, \Big \vert \big[ \softpart f\big](a)\Big\vert$ is uniformly bounded in $\domain$. 
\end{proof}

@@

%\textcolor{magenta}{[we have to change the definition of $k_\text{basic}$ in \S \ref{setting:basic} in $-\frac{q(a')}{p(a)}$.]}

>>>>

% operator under consideration
\newcommand{\volterra}{\mathcal{V}}
\newcommand{\hardpart}{\mathcal{V}_0}
\newcommand{\softpart}{\mathcal{V}_\star}
\newcommand{\hardker}{k_0}
\newcommand{\softker}{k_\star}
\newcommand{\solproto}{f_0}
\newcommand{\solptb}{f_\star}

@@

Since $\softpart$ is a holomorphic Volterra operator, $\softker$ is a holomorphic function on $\domain^2$. We'll allow $\softker(a, a')$ to have a simple pole at $\zeta(a) = 0$, like $\hardker(a, a')$ does, but we won't allow any sharper singularity. We'll also put an exponential bound on how fast $\softker$ grows away from the diagonal, mimicking Condition~\eqref{cond:diag-basic} on $\hardker$. Altogether, we'll require:
\begin{itemize}
\condconst{diag$_\star$}{\epsilon, \lambda_\Delta}\label{cond:eps-lambda} We have
\[ \big| \softker(a, a') \big| \leq \textcolor{magenta}{C_k}\frac{|\zeta(a)-\zeta(a')|^\epsilon}{|\zeta(a)|}\,e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\]
over all $a, a' \in \domain$.
\end{itemize}
Notice that this condition prevents $\softker$ from being separable---unless it's zero, of course.

@@

\begin{proof}
    Let $f\in\singexp{\sigma}{\Lambda}$,
    \begin{align*}
        |\zeta(a)|^{-(\sigma+\epsilon)} \, e^{-\Lambda |\zeta(a)|} \, \Big \vert \big[ \softpart f\big](a)\Big\vert
        &\leq |\zeta(a)|^{-(\sigma+\epsilon)}\, e^{-\Lambda |\zeta(a)|} \int_{\zeta=0}^a |\softker(a,\cdot)|\, |f| \, |d\zeta| \\
        &\leq |\zeta(a)|^{-(\sigma+\epsilon)}\, e^{-\Lambda |\zeta(a)|} \int_{\zeta=0}^a |\softker(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \|f\|_{\sigma,\Lambda} \, |d\zeta| 
    \end{align*}
    By Condition~\eqref{cond:eps-lambda},
    \begin{align*}
         \int_{\zeta=0}^a |\softker(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \, |d\zeta| &\leq C_k \int_{\zeta=0}^a \frac{|\zeta(a)-\zeta|^\epsilon}{|\zeta(a)|} e^{\lambda_\Delta |\zeta(a)-\zeta|} |\zeta|^{\sigma}\, e^{\Lambda|\zeta|}\;|d\zeta|\\
         &=C_k |\zeta(a)|^{\epsilon+\sigma} \int_{0}^1 (1-t)^\epsilon e^{\lambda_\Delta |\zeta(a)|(1-t)} t^{\sigma}\, e^{\Lambda|\zeta(a)| t}\;dt\\
         &=C_k |\zeta(a)|^{\epsilon+\sigma}\, e^{\lambda_\Delta |\zeta(a)|}\,  \int_{0}^1 (1-t)^\epsilon  t^{\sigma}\,e^{(\Lambda-\lambda_\Delta)|\zeta(a)| t}\;dt\\
         &\le C_k |\zeta(a)|^{\epsilon+\sigma}\, e^{\lambda_\Delta |\zeta(a)|}\,e^{(\Lambda-\lambda_\Delta)|\zeta(a)|}\int_{0}^1 (1-t)^\epsilon  t^{\sigma}\;dt.
    \end{align*}
    The last step takes advantage of the assumption that $\Lambda \ge \lambda_\Delta$. Recognizing the integral as an evaluation of the beta function, we can rewrite the bound as
    \[ \int_{\zeta=0}^a |\softker(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \, |d\zeta| \le C_k |\zeta(a)|^{\epsilon+\sigma}\, e^{\Lambda |\zeta(a)|} \frac{\Gamma(\epsilon+1)\Gamma(\sigma+1)}{\Gamma(\sigma+\epsilon+2)}. \]
    Our assumptions that $\epsilon > 0$ and $\sigma > -1$ ensure that the gamma functions are well-defined. Rearranging to get
    \[ |\zeta(a)|^{-(\epsilon+\sigma)}\, e^{-\Lambda |\zeta(a)|} \int_{\zeta=0}^a |\softker(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \, |d\zeta| \le C_k \frac{\Gamma(\epsilon+1)\Gamma(\sigma+1)}{\Gamma(\sigma+\epsilon+2)}, \]
    we conclude that $|\zeta(a)|^{-\sigma-\epsilon} \, e^{-\Lambda |\zeta(a)|} \, \Big \vert \big[ \softpart f\big](a)\Big\vert$ is uniformly bounded in $\domain$. 
\end{proof}

@@

%\textcolor{magenta}{[we have to change the definition of $\hardker$ in \S \ref{setting:basic} in $-\frac{q(a')}{p(a)}$.]}
